Applied Measure Theory for Probabilistic Modeling

### 2022-05-20 paper/paper.tex
Update paper/paper.tex
Co-authored-by: Moritz Schauer <moritzschauer@web.de>

 As the reader might now suspect, such known events form a $\sigma$-algebra. In particular, for each random variable $\bX$ there is a $\sigma$-algebra associated with $\bX$ that encodes what else we know knowing $\bX$ and how we should assign (conditional) probabilities to other events knowing $\bX$.

 This is a very relevant question for probabilistic programming tasks and causal inference. But we've already mentioned that \verb|MeasureTheory| does not explicitly represent $\sigma$-algebras. Instead, questions like these can be addressed using \emph{kernels} (Section~\ref{Kernels}). These give a way to reason about local behavior, and be much more computationally efficient.

>>>>

 As the reader might now suspect, such systems of known events form a $\sigma$-algebra. In particular, for each random variable $\bX$ there is a $\sigma$-algebra associated with $\bX$ that encodes what else we know knowing $\bX$ and how we should assign (conditional) probabilities to other events knowing $\bX$.

 This is a very relevant question for probabilistic programming tasks and causal inference. But we've already mentioned that \verb|MeasureTheory| does not explicitly represent $\sigma$-algebras. Instead, questions like these can be addressed using \emph{kernels} (Section~\ref{Kernels}), structures which can hold the conditional probabilities given we find a way to assign them in a computationally efficient way.
